### 2022-06-02 main/chapter_2ljets.tex
add vrss figure

>>>>

Figure~\ref{fig:2ljets_vrss}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrss_VR_SS_EWK_met_Sign.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrss_VR_SS_EWKMC_met_Sign.png}
\caption{}
\end{subfigure}
\caption[
Same-sign validation with Matrix Method and Monte Carlo fake estimates
]{%
Same-sign validation with (a) Matrix Method and (b) Monte Carlo fake estimates.
Errors are statistical summed in quadrature with variations in Matrix Method
sample weights.
Those Matrix Method variations are coupled between bins, meaning that the
directed differences between bins are less significant than an independent
combination.
% thesis_project/2ljets/vrss_plots/PAM_FNP_50pc.pdf
The figure in (a) was included in an early draft of the paper as evidence to
the quality of the Matrix Method fake/non-prompt estimate.
On the decision of our editorial board, it was removed after validation studies
showed that adding an additional $50\%$ uncertainty to fake/non-prompt yields
made an insignificant difference to the results.
This variation was coupled between all bins.
Differences were assessed by the resulting change in exclusion contours,
which mostly moved by less than their plotted line width.
}
\label{fig:2ljets_vrss}
\end{figure}
